Eye Fitting Straight Lines in the Modern Era (JCGS-22-045)

### 2022-08-02 analysis/you-draw-it-eyefitting-analysis.Rmd
working on revisions

@@

eyefitting_parameter_details <- read_csv("eyefitting_parameter_details.csv")
eyefitting_parameter_details %>% knitr::kable()

@@

# write.csv(eyefitting_sim_data, "eyefitting-simulated-data.csv", row.names = F, na = "")

@@

There are a total of `length(unique(eyefitting_model_data$participant_id))` participants and `length(unique(eyefitting_model_data$participant_id))` 'You Draw It' plots completed.

@@

# Plot Predictions
eyefitting.lmer.plot <- eyefitting.preds.lmer %>%
  filter((parm_id %in% c("F", "N", "S") | (x <= 16 & x >= 4))) %>%
  mutate(parm_id = factor(parm_id, levels = c("S", "F", "V", "N"))) %>%
  dplyr::rename(`Parameter Choice` = parm_id) %>%
  ggplot(aes(x = x)) +
  geom_line(data = eyefitting_model_data %>% mutate(parm_id = factor(parm_id, levels = c("S", "F", "V", "N"))) %>% dplyr::rename(`Parameter Choice` = parm_id), 
            aes(x = x, y = residual_ols_drawn, group = plot_id, color = "OLS"), alpha = 0.2) +
  geom_line(data = eyefitting_model_data %>% mutate(parm_id = factor(parm_id, levels = c("S", "F", "V", "N"))) %>% dplyr::rename(`Parameter Choice` = parm_id), 
            aes(x = x, y = residual_pca_drawn, group = plot_id, color = "PCA"), alpha = 0.2) +
  geom_ribbon(aes(ymin = asymp.LCL.ols, ymax = asymp.UCL.ols, fill = "OLS"), color = NA, alpha = 0.4) +
  geom_line(aes(y = emmean.ols, color = "OLS")) +
  geom_ribbon(aes(ymin = asymp.LCL.pca, ymax = asymp.UCL.pca, fill = "PA"), color = NA, alpha = 0.4) +
  geom_line(aes(y = emmean.pca, color = "PCA")) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  facet_wrap(~`Parameter Choice`, ncol = 1) +
  theme_bw(base_size = 14) +
  theme(aspect.ratio = 1,
        legend.position = "right",
        plot.title   = element_text(size = 12, hjust = 0),
        axis.text    = element_text(size = 12),
        axis.title   = element_text(size = 12),
        legend.title = element_text(size = 12),
        legend.text  = element_text(size = 12),
        # strip.text = element_text(size = 5, margin = margin(0.05,0,0.05,0, "cm")),
        # strip.background = element_rect(size = 0.5),
        legend.key.size = unit(1, "line")
        ) +
  scale_y_continuous("Residual") +
  scale_color_manual("Individual participant \nresiduals", values = c("steelblue", "orange"), labels = c("OLS", "PCA")) +
  scale_fill_manual("LMER fitted trend", values = c("steelblue", "orange"), labels = c("OLS", "PA"))

@@

# Plot Predictions
eyefitting.gamm.plot <- eyefitting.grid.gamm %>%
  filter((parm_id %in% c("F", "N", "S") | (x <= 16 & x >= 4))) %>%
  mutate(parm_id = factor(parm_id, levels = c("S", "F", "V", "N"))) %>%
  dplyr::rename(`Parameter Choice` = parm_id) %>%
  ggplot(aes(x = x)) +
  geom_line(data = eyefitting_model_data %>% mutate(parm_id = factor(parm_id, levels = c("S", "F", "V", "N"))) %>% dplyr::rename(`Parameter Choice` = parm_id), aes(x = x, y = residual_ols_drawn, group = plot_id, color = "OLS"), alpha = 0.2) +
  geom_line(data = eyefitting_model_data %>% mutate(parm_id = factor(parm_id, levels = c("S", "F", "V", "N"))) %>% dplyr::rename(`Parameter Choice` = parm_id), aes(x = x, y = residual_pca_drawn, group = plot_id, color = "PA"), alpha = 0.2) +
  geom_ribbon(aes(ymin = ols.lower, ymax = ols.upper, fill = "OLS"), color = NA, alpha = 0.4) +
  geom_line(aes(y = ols.pred, color = "OLS")) +
  geom_ribbon(aes(ymin = pca.lower, ymax = pca.upper, fill = "PA"), color = NA, alpha = 0.4) +
  geom_line(aes(y = pca.pred, color = "PA")) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  facet_wrap(~`Parameter Choice`, ncol = 1) +
  theme_bw(base_size = 14) +
  theme(aspect.ratio = 1,
        legend.position = "right",
        plot.title   = element_text(size = 12, hjust = 0),
        axis.text    = element_text(size = 12),
        axis.title   = element_text(size = 12),
        legend.title = element_text(size = 12),
        legend.text  = element_text(size = 12),
        # strip.text = element_text(size = 5, margin = margin(0.05,0,0.05,0, "cm")),
        # strip.background = element_rect(size = 0.5),
        legend.key.size = unit(1, "line")
        ) +
  scale_y_continuous("Residual") +
  scale_color_manual("Individual participant \nresiduals", values = c("steelblue", "orange"), labels = c("OLS", "PCA")) +
  scale_fill_manual("GAMM fitted trend", values = c("steelblue", "orange"), labels = c("OLS", "PCA")) 
eyefitting.gamm.plot
```

>>>>

<!-- ## GET DATA FROM DATABASE -->

<!-- ```{r db} -->
<!-- library(RSQLite) -->
<!-- library(DBI) -->
<!-- library(digest) -->
<!-- library(lubridate) -->

<!-- last_date <- as.numeric(as_datetime("2021-05-18 18:00:00 CDT")) -->

<!-- # Connect to database -->
<!-- filename <- "you_draw_it_data.db" -->
<!-- sqlite.driver <- dbDriver("SQLite") -->
<!-- db_con <- dbConnect(sqlite.driver, dbname = filename) -->
<!-- # dbListTables(db_con) -->

<!-- # Import eyefitting parameter details -->
<!-- eyefitting_parameter_details <- dbReadTable(db_con,"eyefitting_parameter_details") %>% -->
<!--   mutate(parm_id = as.factor(as.character(parm_id))) -->

<!-- # Import user data -->
<!-- users <- dbReadTable(db_con,"users") %>% -->
<!--   filter(study_starttime > 1620152231, study_starttime < last_date) %>% -->
<!--   select(-ip_address) %>% -->
<!--   rowwise() %>% -->
<!--   mutate(participant_id = as.factor(digest(paste(nick_name, study_starttime)))) -->

<!-- # Import exponential prediction feedback data -->
<!-- eyefitting_feedback_data <- dbReadTable(db_con,"feedback") %>% -->
<!--   filter(study_starttime > 1620152231, study_starttime < last_date) %>% -->
<!--   filter(parm_id %in% c("S", "F", "V", "N")) %>% -->
<!--   rename(yols = y) %>% -->
<!--   rowwise() %>% -->
<!--   mutate(participant_id = as.factor(digest(paste(nick_name, study_starttime)))) %>% -->
<!--   left_join(users, by = c("participant_id", "nick_name", "study_starttime")) %>% -->
<!--   filter(recruitment != "I am the researcher") %>% -->
<!--   rowwise() %>% -->
<!--   mutate(plot_id = as.factor(digest(paste(nick_name, start_time, end_time)))) %>% -->
<!--   select(study_starttime, participant_id, nick_name, plot_id, start_time, end_time, parm_id, x, yols, ydrawn, age, gender, academic_study, recruitment) -->

<!-- factorCols <- c("nick_name", "study_starttime", "age", "gender", "academic_study", -->
<!--                 "recruitment", "participant_id", "parm_id", "plot_id") -->
<!-- eyefitting_feedback_data[,factorCols] <- lapply(eyefitting_feedback_data[,factorCols], factor) -->
<!-- # write.csv(eyefitting_feedback_data, file = "eyefitting-feedback-data.csv", row.names = F, na = "") -->

<!-- # Import exponential prediction simulated data -->
<!-- eyefitting_simulated_data <- dbReadTable(db_con,"simulated_data") %>% -->
<!--   filter(study_starttime > 1620152231, study_starttime < last_date) %>% -->
<!--   filter(parm_id %in% c("S", "F", "V", "N")) %>% -->
<!--   rowwise() %>% -->
<!--   mutate(participant_id = as.factor(digest(paste(nick_name, study_starttime)))) %>% -->
<!--   left_join(users, by = c("participant_id", "nick_name", "study_starttime")) %>% -->
<!--   filter(recruitment != "I am the researcher") -->

<!-- factorCols <- c("nick_name", "dataset", "study_starttime", "age", "gender", "academic_study", -->
<!--                 "recruitment", "participant_id", "parm_id") -->
<!-- eyefitting_simulated_data[,factorCols] <- lapply(eyefitting_simulated_data[,factorCols], factor) -->
<!-- # write.csv(eyefitting_simulated_data, file = "eyefitting-simulated-data.csv", row.names = F, na = "") -->

<!-- # Disconnect from database -->
<!-- dbDisconnect(db_con) -->
<!-- length(unique(eyefitting_feedback_data$participant_id)) -->
<!-- length(unique(eyefitting_feedback_data$plot_id)) -->
<!-- ``` -->

@@

eyefitting_parameter_details <- read_csv("eyefitting-parameter-details.csv")
eyefitting_parameter_details %>% knitr::kable()

@@

write.csv(eyefitting_sim_data, "eyefitting-simulated-data.csv", row.names = F, na = "")

@@

There are a total of `r length(unique(eyefitting_model_data$participant_id))` participants and `r length(unique(eyefitting_model_data$participant_id))` 'You Draw It' plots completed.

@@

# Plot Predictions
eyefitting.lmer.plot <- eyefitting.preds.lmer %>%
  filter((parm_id %in% c("F", "N", "S") | (x <= 16 & x >= 4))) %>%
  mutate(parm_id = factor(parm_id, levels = c("S", "F", "V", "N"))) %>%
  dplyr::rename(`Parameter Choice` = parm_id) %>%
  ggplot(aes(x = x)) +
  geom_line(data = eyefitting_model_data %>% mutate(parm_id = factor(parm_id, levels = c("S", "F", "V", "N"))) %>% dplyr::rename(`Parameter Choice` = parm_id), 
            aes(x = x, y = residual_ols_drawn, group = plot_id, color = "OLS"), alpha = 0.2) +
  geom_line(data = eyefitting_model_data %>% mutate(parm_id = factor(parm_id, levels = c("S", "F", "V", "N"))) %>% dplyr::rename(`Parameter Choice` = parm_id), 
            aes(x = x, y = residual_pca_drawn, group = plot_id, color = "PCA"), alpha = 0.2) +
  geom_ribbon(aes(ymin = asymp.LCL.ols, ymax = asymp.UCL.ols, fill = "OLS"), color = NA, alpha = 0.4) +
  geom_line(aes(y = emmean.ols, color = "OLS")) +
  geom_ribbon(aes(ymin = asymp.LCL.pca, ymax = asymp.UCL.pca, fill = "PA"), color = NA, alpha = 0.4) +
  geom_line(aes(y = emmean.pca, color = "PCA")) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  facet_wrap(~`Parameter Choice`, ncol = 4) +
  theme_bw(base_size = 14) +
  theme(aspect.ratio = 1,
        legend.position = "right",
        plot.title   = element_text(size = 12, hjust = 0),
        axis.text    = element_text(size = 12),
        axis.title   = element_text(size = 12),
        legend.title = element_text(size = 12),
        legend.text  = element_text(size = 12),
        # strip.text = element_text(size = 5, margin = margin(0.05,0,0.05,0, "cm")),
        # strip.background = element_rect(size = 0.5),
        legend.key.size = unit(1, "line")
        ) +
  scale_y_continuous("Residual") +
  scale_color_manual("Individual participant \nresiduals", values = c("steelblue", "orange"), labels = c("OLS", "PCA")) +
  scale_fill_manual("LMER fitted trend", values = c("steelblue", "orange"), labels = c("OLS", "PA"))

@@

# Plot Predictions
eyefitting.gamm.plot <- eyefitting.grid.gamm %>%
  filter((parm_id %in% c("F", "N", "S") | (x <= 16 & x >= 4))) %>%
  mutate(parm_id = factor(parm_id, levels = c("S", "F", "V", "N"))) %>%
  dplyr::rename(`Parameter Choice` = parm_id) %>%
  ggplot(aes(x = x)) +
  geom_line(data = eyefitting_model_data %>% mutate(parm_id = factor(parm_id, levels = c("S", "F", "V", "N"))) %>% dplyr::rename(`Parameter Choice` = parm_id), aes(x = x, y = residual_ols_drawn, group = plot_id, color = "OLS"), alpha = 0.2) +
  geom_line(data = eyefitting_model_data %>% mutate(parm_id = factor(parm_id, levels = c("S", "F", "V", "N"))) %>% dplyr::rename(`Parameter Choice` = parm_id), aes(x = x, y = residual_pca_drawn, group = plot_id, color = "PA"), alpha = 0.2) +
  geom_ribbon(aes(ymin = ols.lower, ymax = ols.upper, fill = "OLS"), color = NA, alpha = 0.4) +
  geom_line(aes(y = ols.pred, color = "OLS")) +
  geom_ribbon(aes(ymin = pca.lower, ymax = pca.upper, fill = "PA"), color = NA, alpha = 0.4) +
  geom_line(aes(y = pca.pred, color = "PA")) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  facet_wrap(~`Parameter Choice`, ncol = 4) +
  theme_bw(base_size = 14) +
  theme(aspect.ratio = 1,
        legend.position = "right",
        plot.title   = element_text(size = 12, hjust = 0),
        axis.text    = element_text(size = 12),
        axis.title   = element_text(size = 12),
        legend.title = element_text(size = 12),
        legend.text  = element_text(size = 12),
        # strip.text = element_text(size = 5, margin = margin(0.05,0,0.05,0, "cm")),
        # strip.background = element_rect(size = 0.5),
        legend.key.size = unit(1, "line")
        ) +
  scale_y_continuous("Residual") +
  scale_color_manual("Individual participant \nresiduals", values = c("steelblue", "orange"), labels = c("OLS", "PCA")) +
  scale_fill_manual("GAMM fitted trend", values = c("steelblue", "orange"), labels = c("OLS", "PCA")) 
eyefitting.gamm.plot
```
